Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-06-26 latex/paper.tex
reformat pre
add group velocity

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-26 15:07:24
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Chao-Yu Chen${}^{3}$}
\author{Zhi-Xin Guo${}^{3}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen}
\author{Hong-Jun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

\begin{table*}
  \caption{\label{tab:table1}
    Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}
      Name
           & Minimal period
           & Symmetry
           & $E_c$ in Guo
           & $E_c$ in MD
           & Buckling Feature                                                                       \\
      \hline
      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

\begin{table*}
  \caption{\label{tab:table2}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}

            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$
            &
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$                                                                \\
      \hline
      2l1   & 11.6                & 6.5  & 43.9\% & 2l2      & 1.5  & 1.2  & 20.0\% \\
      2l3   & 5.0                 & 9.7  & 48.5\% & 2lr3     & 8.2  & 3.5  & 57.3\% \\
      2lh   & 2.0                 & 2.5  & 20.0\% & 3l1      & 11.5 & 2.9  & 74.8\% \\
      3l2   & 10.2                & 5.2  & 49.0\% & 4l1      & 10.2 & 3.4  & 66.7\% \\
      5l1   & 11.7                & 5.7  & 51.3\% & 6l1      & 10.3 & 7.8  & 24.3\% \\
      8l1   & 13.2                & 14.9 & 11.4\% & 10l1     & 13.3 & 13.5 & 1.5\%  \\
      Si111 & 33.6                & 34.7 & 3.2\%  & Silicene & 11.4 & 11.6 & 1.7\%  \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/gv}
  \caption{\label{fig:gv} (color online)Group Velocity.}
\end{figure}

@@

The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures. In previous work we have proven that  phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}. The participation ratio of all the structures as shown in FIG.\ref{fig:pr_direction}.PR of both Silicene and 2l1 structures are exactly the same , suggesting that every phonon has been participated by all the atoms ,which means there's no localization. The others all present localization but that of 2l2 is isotropic while  PR is larger for armchair of 2l3 than that of zigag which is consist with their thermal conductivity.

@@

The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering. Considering three- phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-26 23:08:02
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Chao-Yu Chen${}^{3}$}
\author{Zhi-Xin Guo${}^{3}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen}
\author{Hong-Jun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

\begin{table*}
  \caption{\label{tab:table1}
    Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}
      Name
           & Minimal period
           & Symmetry
           & $E_c$ in Guo
           & $E_c$ in MD
           & Buckling Feature                                                                       \\
      \hline
      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
    \end{tabular}
  \end{ruledtabular}

\end{table*}

@@

\begin{table*}
  \caption{\label{tab:table2}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$
            &
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$                                                                \\
      \hline
      2l1   & 11.6                & 6.5  & 43.9\% & 2l2      & 1.5  & 1.2  & 20.0\% \\
      2l3   & 5.0                 & 9.7  & 48.5\% & 2lr3     & 8.2  & 3.5  & 57.3\% \\
      2lh   & 2.0                 & 2.5  & 20.0\% & 3l1      & 11.5 & 2.9  & 74.8\% \\
      3l2   & 10.2                & 5.2  & 49.0\% & 4l1      & 10.2 & 3.4  & 66.7\% \\
      5l1   & 11.7                & 5.7  & 51.3\% & 6l1      & 10.3 & 7.8  & 24.3\% \\
      8l1   & 13.2                & 14.9 & 11.4\% & 10l1     & 13.3 & 13.5 & 1.5\%  \\
      Si111 & 33.6                & 34.7 & 3.2\%  & Silicene & 11.4 & 11.6 & 1.7\%  \\
    \end{tabular}
  \end{ruledtabular}

\end{table*}

@@

The thermal conductivity tensor could be calculated with

\begin{equation}
  \kappa^{\alpha\beta} = \sum_{k \sigma}{c_{k \sigma}v^{\alpha}_{k \sigma}v^{\beta}_{k \sigma}\tau_{k \sigma}} \label{eq:kappasum}
\end{equation}

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $tau_{k \sigma}$ is phonon lifetime. The anisotropy could derive from these factors and it's worth finding the most important ones.

Heat capacity has no contribution to anisotropy. The average heat capacity is shown in Fig.\ref{fig:cv} and it's obviously that there's no difference in the value of the two directions.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/cv}
  \caption{\label{fig:cv} (color online)Average Phonon heat capacity. The red bar present for the value of zigzag direction and yellow represent for that of armchiar direction. }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/gv}{}
  \caption{\label{fig:gv} (color online)Group Velocity.}
\end{figure}

@@

The anisotroy of group velocity derived from the localization of phonons along that directoin. The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures. In previous work we have proven that  phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}. The participation ratio of all the structures as shown in FIG.\ref{fig:pr_direction}.PR of both Silicene and 2l1 structures are exactly the same , suggesting that every phonon has been participated by all the atoms ,which means there's no localization. The others all present localization but that of 2l2 is isotropic while  PR is larger for armchair of 2l3 than that of zigag which is consist with their thermal conductivity.

@@

The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering. Considering three-phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity.
